Diffantom: a software layer to build digital phantoms of whole-brain diffusion MRI

### 2015-07-23 paper/main.tex
fixes for submitting to FINF
fix typo
changes proposed by AS

%\setcitestyle{square}
\usepackage{url,lineno,microtype}
\usepackage[colorlinks=true,linkcolor=black, citecolor=black!80, urlcolor=black!80]{hyperref}
\usepackage{doi}
\usepackage[onehalfspacing]{setspace}
\usepackage[toc,nomain,acronym,shortcuts,translate=false]{glossaries}

\def\keyFont{\fontsize{7}{9}\helveticabold }
\def\firstAuthorLast{Esteban {et~al.}} %use et al only if is more than 1 author
\def\Authors{Oscar Esteban\,$^{1,2,*}$, Emmanuel Caruyer\,$^{3}$, Alessandro Daducci\,$^{4}$, Meritxell Bach-Cuadra\,$^{4,5}$,%
M.-Jes\'us Ledesma-Carbayo\,$^{1,2}$ and Andres Santos\,$^{1,2}$}

@@

\newcommand{\e}[1]{\ensuremath{\;\cdot\,}10\ensuremath{^{#1}}}
\begin{document}

@@

\section*{Introduction}
Fiber tracking on \gls*{dmri} data has become an important application in the in-vivo investigation
  of the structural configuration of fiber bundles at the macro-scale.
The final outcome of such applications, called tractography, is fundamental to gain information about
  \gls*{wm} morphology in neurosurgical planning \citep{golby_interactive_2011},
  post-surgery evaluations \citep{toda_utility_2014},
  and the study of neurological diseases such as multiple sclerosis, and Alzheimer's disease
  \citep{chua_diffusion_2008}.
Tractography is also crucial in the analysis of structural brain networks using graph theory.
These analyses have been successfully applied in the definition of the unique subject-wise patterns of connectivity
  \citep{sporns_human_2005}, the assessment of neurological diseases \citep{griffa_structural_2013}, and in the
  study of the link between structural and functional connectivity \citep{messe_predicting_2015}.
However, the development of the field is limited by the lack of gold standards to test and compare the
  wide range of algorithms and processing methodologies available.
In this report we present \emph{diffantom}, an \emph{in-silico} dataset to assess tractography pipelines using
  real data as source of whole-brain micro-structural information.
We also provide a full software layer to produce \emph{diffantoms} from real \gls*{dmri} datasets
  drawn from the \gls*{hcp}.
This dataset enables the following evaluations of standard connectivity pipelines:
\begin{itemize}
  \item Comparisons of the impact of the different diffusion sampling schemes on the local micro-structure
  model of choice and the subsequent global tractography outcome.
  \item Investigations on the effects of the different artifacts (noise, \glspl*{pve} and \gls*{csf} contamination,
    susceptibility-derived warping, Eddy-currents-derived distortions, etc.) at both local and global levels.
  \item Determine of the \acrfull*{roc} of connectivity pipelines.
  \item Generation of synthetic connectivity networks to test graph theory analyses.
  \item Simulation of pathological brains (i.e. tumors as in \cite{kaus_simulation_2000}).
\end{itemize}

\section*{Background}
The assessment of tractography from \gls*{dmri} data is challenging due to
  the lack of a gold standard.
Large efforts have been devoted to the development of physical phantoms
  \citep{lin_validation_2001,campbell_flowbased_2005,perrin_validation_2005,fieremans_simulation_2008,tournier_resolving_2008}.
\cite{cote_tractometer_2013} conducted a thorough review of tractography methodologies using the
  so-called \emph{FiberCup} phantom \citep{poupon_new_2008,fillard_quantitative_2011}.
These phantoms are appropriate to evaluate the resolution of fiber crossings and accuracy of
  direction-independent scalar parameters in very simplistic geometries.
Since the complexity of whole-brain tractography is unaccountable with current materials and proposed
  methodologies to build physical phantoms, digital simulations are increasingly popular.
Early digital phantoms started with simulation of simple geometries as well
  \citep{basser_in_2000,goessl_fiber_2002,tournier_limitations_2002,leemans_mathematical_2005}
  to evaluate resolution of fiber crossings.
These tools generally implemented the multi-tensor model \citep{alexander_analysis_2001,tuch_high_2002}
  to simulate fibers crossing, fanning, kissing, etc.
\cite{close_software_2009} presented the \emph{Numerical Fibre Generator}, a software to simulate
  spherical shapes filled with digital fiber-tracts.
\cite{caruyer_phantomas_2014} proposed \emph{Phantomas} to simulate any kind of analytic geometry
  inside a sphere.
\emph{Phantomas} models diffusion by a restricted and a hindered compartment, similar to
  \citep{assaf_composite_2005}.
\cite{wilkins_fiber_2014} proposed a whole-brain simulated phantom derived from voxel-wise orientation
  of fibers averaged from real \gls*{dmri} scans and the multi-tensor model with a compartment of
  isotropic-diffusion.
Recently, \cite{neher_fiberfox_2014} proposed \emph{FiberFox}, a visualization software to develop
  complex geometries and their analytical description.
Once the geometries are obtained, the software generates the corresponding \gls*{dmri} signal with a
  methodology very close to that implemented in \emph{Phantomas}.

@@

\noindent\textbf{\textit{Data Generation\textcolon}\label{sec:data_generation}}
The methods to generate \emph{diffantoms} are rooted in the work of \cite{wilkins_fiber_2014}, and
  described in \autoref{fig:figure1}.
\emph{Diffantom} integrates two major improvements with respect to \citep{wilkins_fiber_2014}.
First, since we use a dataset from the \gls*{hcp} as input, data are corrected for the most relevant distortions.
\cite{wilkins_fiber_2014} explicitly state that their original data were not subjected to certain distortion
  corrections, and thus, generated data are affected correspondingly.
Second improvement is a more advanced signal model to generate the phantom using
  \emph{phantomas} \citep{caruyer_phantomas_2014}.

The simulation process begins with generating a micro-structural model from real data (\autoref{fig:figure1}).
On one hand, the software requires up to five volume fractions $\{T_{1\,\cdots\,5}\}$ corresponding to the free-diffusion
  compartments that will be simulated.
These isotropic fraction maps use the \emph{5TT format} established with \emph{MRTrix3} \citep{tournier_mrtrix_2012}
  that describes the structure of the brain in the following order: \gls*{cgm}, \gls*{dgm}, \gls*{wm}, \gls*{csf},
  and abnormal tissue.
Since we simulated a healthy subject, the last fraction map is empty and can be omitted.
On the other hand, the hindered-diffusion compartments are specified by up to three volume fractions $\{F_{1\,\cdots\,3}\}$
  of three single fiber populations per voxel along with their corresponding direction maps $\{V_{1\,\cdots\,3}\}$.
The process to obtain these inputs is described as follows:
1) The fiber orientation maps $\{V_{1\,\cdots\,3}\}$ and their corresponding fiber-fraction maps are
  obtained using the ball-and-stick model for multi-shell data of BEDPOSTX \citep{jbabdi_modelbased_2012}
  on the \gls*{dmri} data of a certain \gls*{hcp} subject.
2) We obtain a \gls*{fa} map after fitting a tensor model with \emph{MRTrix3}.
3) The original fiber-fractions and the \gls*{fa} map are smoothed with a non-local means filter included
  in \emph{dipy} \citep{garyfallis_dipy_2011}.
4) By combining with \emph{MRTrix} the volume fraction maps computed with FSL FAST \citep{zhang_segmentation_2001} and
  FSL FIRST \citep{patenaude_bayesian_2011}, we obtain the macro-structural 5TT map of the subject.
5) The objects obtained in the previous steps are combined as described in the \nameref{sec:appendix} to generate the
  outcome presented in \autoref{fig:figure1}, box A.

Once a micro-structural model of the volume has been synthesized, a map of \glspl{fod} is computed using spherical
  convolution of the single fiber response and the fiber orientation maps $\{V_{1\,\cdots\,3}\}$, weighted by the
  corresponding fiber-fractions $\{F_{1\,\cdots\,3}\}$.
A close-up showing how the \glspl{fod} map looks is presented in \autoref{fig:figure1}.
The single fiber response is a Gaussian diffusion tensor with axial symmetry and eigenvalues $\lambda_1=$ 2.2\e{-3}
  and $\lambda_{2,3}=$ 0.2\e{-3} [mm$^2$s$^{-1}$].
The resulting \glspl{fod} map is then combined with the isotropic compartments corresponding to $\{T_{1\,\cdots\,5}\}$
  before generating the signal using \emph{phantomas} \citep{caruyer_phantomas_2014}.
By default, diffusion data are generated using a scheme of 100 directions distributed in one shell with uniform
  coverage \citep{caruyer_design_2013}.
Custom one- or multi-shell schemes can be generated supplying the tables of corresponding $b$-vectors and $b$-values.
Rician noise is also included in \emph{phantomas}, and can be set by the user.
The default value for \gls*{snr} is preset to 90.0.
\Gls*{csf} was simulated with a unique compartment with isotropic diffusivity $D_{CSF}$ of 3.0\e{-3} [mm$^2$s$^{-1}$].
Conversely, \Gls*{wm} and \gls*{gm} included one isotropic compartment with $D_{WM} =$ 2.0\e{-4}, $D_{cGM} =$ 7.0\e{-4}
  and $D_{dGM} =$ 9.0\e{-4}, respectively [mm$^2$s$^{-1}$].
All these values for diffusivity (and the corresponding to the single-fiber response) can be modified by the user with
  custom settings.

@@

\noindent\textbf{\textit{Discussion\textcolon}}\label{sec:discussion} %
Whole-brain, realistic \gls*{dmri} phantoms are necessary in the developing field of structural
  connectomics.
The \emph{diffantom} is a derivative of \citep{wilkins_fiber_2014} in terms of methodology for
  simulation with two major improvements: the correctness of the \emph{minimally preprocessed} data
  \citep{glasser_minimal_2013} released within the \gls*{hcp}, and a more realistic diffusion
  model.
A possible competitor to \emph{diffantom} is the ground-truth data generated by the organizers of the
  Tractography Challenge held in the ISMRM 2015\footnote{\url{http://www.tractometer.org/ismrm_2015_challenge/}}.
Similarly to \emph{diffantom}, one \gls*{hcp} dataset is used as source of structural information.
However, in this case 25 fiber bundles were manually segmented to obtain a summary tractogram.
Then, making use of \emph{FiberFox}, the segmentation of each bundle is mapped to an analytical description
  which is fed into \emph{phantomas}.
While this phantom is designed for the bundle-wise evaluation of tractography (with scores such as geometrical coverage,
  valid connections, invalid connections, missed connections, etc. \citep{cote_tractometer_2013}),
  \emph{diffantom} is intended for the connectome-wise evaluation of results, yielding tractography with
  a large number of bundles.
Therefore, \emph{diffantom} and \emph{FiberFox} are complementary as the hypotheses that can be investigated are different.
Moreover, \emph{diffantom} does not require costly manual segmentation of bundles, highly demanding in terms of physiology
  expertise and operation time.
This facilitates the use of \emph{diffantom} as a factory of whole-brain diffusion phantoms.
Lastly, since the gradient scheme can be set by the user, \emph{diffantom} can be seen as a mean to translate the so-called
  \emph{b-matrix} of the \gls*{hcp} to any target scheme.

@@

\section*{Data Sharing}
The first \emph{diffantom} is available under the \gls*{cc0} in {\color{red} (dryad?)}.
The associated software to ``\emph{diffantomize}'' real \gls*{dmri} data is available at \url{https://github.com/oesteban/diffantom}
  under an MIT license.
\emph{Phantomas} is available in \url{https://github.com/ecaruyer/phantomas} under the revised-BSD license.

@@

\section*{Author Contributions}
All the authors contributed to this study.
OE designed the data generation procedure, implemented the processing pipelines and generated the example dataset.
EC implemented \emph{phantomas} \citep{caruyer_phantomas_2014}, helped integrate the project with the simulation routines.
OE, EC, AD thoroughly discussed and framed the aptness of the data in the community.
AD, MBC, MJLC, and AS interpreted the resulting datasets.
MBC, MJLC, and AS advised on all aspects of the study.

@@

\bibliographystyle{frontiers/frontiersinSCNS_ENG_HUMS}
%\bibliographystyle{frontiersinHLTH&FPHY} % for Health and Physics articles
\bibliography{Remote}

@@

\glsresetall

\section*{Appendix}\label{sec:appendix}
Let $\{T'_{1\,\cdots\,5}\}$ be the set of original fractions maps obtained with the combined use of FAST and FIRST, FA the
  \gls*{fa} map obtained from the original \gls*{dmri} data, and $\{V_{1\,\cdots\,3}, F'_{1\,\cdots\,3}\}$ the direction
  maps $V_i$ of restricted diffusion by fibers with their estimated volume fractions $F'_i$ calculated with BEDPOSTX.
The final $\{T_{1\,\cdots\,5}\}$ maps of isotropic fractions are computed as follows:

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\linewidth]{figures/figure01A}
\includegraphics[width=\linewidth]{figures/figure01B}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:figure1} Figure \arabic{figure}. }%
{\textbf{Generation of \emph{diffantoms}:} First, a micro-structural model is generated as described
  in the \nameref{sec:data_generation} subsection.
Please note the piece-wise linear function of the color scale to enable visibility of small volume fractions.
This micro-structural model is fed into a simulation block that generates the final \gls*{dmri} dataset
  as described in the second block.
}
\end{figure}

>>>>

\usepackage[mode=buildnew]{standalone}
\usepackage{tikz}
%\setcitestyle{square}
\usepackage{url,lineno,microtype}
\usepackage[toc,nomain,acronym,shortcuts,translate=false]{glossaries}
\usepackage[colorlinks=true,linkcolor=black, citecolor=black!80, urlcolor=black!80]{hyperref}
\usepackage{doi}
\usepackage[onehalfspacing]{setspace}

\def\keyFont{\fontsize{7}{9}\helveticabold }
\def\firstAuthorLast{Esteban {et~al.}} %use et al only if is more than 1 author
\def\Authors{Oscar Esteban\,$^{1,2,*}$, Emmanuel Caruyer\,$^{3}$, Alessandro Daducci\,$^{4}$, Meritxell Bach-Cuadra\,$^{4,5}$,%
Mar\'ia-J. Ledesma-Carbayo\,$^{1,2}$ and Andres Santos\,$^{1,2}$}

@@

\newcommand{\e}[1]{\ensuremath{\;\cdot\,}10\ensuremath{^{#1}}}
\newcommand*\glslines[2][]{\glslink[#1]{#2}{\glsdisp{#2}{\acrlong{#2} --\glsentryshort{#2}--}}}

\begin{document}

@@

\section*{Introduction}
Fiber tracking on \gls*{dmri} data has become an important application in the in-vivo investigation
  of the structural configuration of fiber bundles at the macro-scale.
The final outcome of such applications, called tractography, is fundamental to gain information about
  \gls*{wm} morphology in neurosurgical planning \citep{golby_interactive_2011},
  post-surgery evaluations \citep{toda_utility_2014},
  and the study of neurological diseases such as multiple sclerosis and Alzheimer's disease
  \citep{chua_diffusion_2008}.
Tractography is also crucial in the analysis of structural brain networks using graph theory.
These analyses have been successfully applied in the definition of the unique subject-wise patterns of connectivity
  \citep{sporns_human_2005}, the assessment of neurological diseases \citep{griffa_structural_2013}, and in the
  study of the link between structural and functional connectivity \citep{messe_predicting_2015}.
However, the development of the field is limited by the lack of gold standards to test and compare the
  wide range of algorithms and processing methodologies available.
In this report we present \emph{diffantom}, an \emph{in-silico} dataset to assess tractography pipelines using
  real data as source of whole-brain microstructural information.
We also provide a full software layer to produce \emph{diffantoms} from real \gls*{dmri} datasets
  drawn from the \gls*{hcp}.
The \emph{diffantom} enables the following evaluations of standard connectivity pipelines:
\begin{itemize}
  \item Comparisons of the impact of different diffusion sampling schemes on the local micro-structure
  model of choice and the subsequent global tractography outcome.
  \item Investigations on the effects of the different artifacts (noise, \acrlong{pve} and \glslines{csf} contamination,
    susceptibility-derived warping, Eddy-currents-derived distortions, etc.) at both local and global levels.
  \item Characterizing the \acrfull*{roc} of connectivity pipelines.
  \item Generation of synthetic connectivity networks to test graph theory analyses.
  \item Simulation of pathological brains (e.g. tumors as in \cite{kaus_simulation_2000}).
\end{itemize}

\section*{Background}
The assessment of tractography from \gls*{dmri} data is challenging due to
  the lack of a gold standard.
Large efforts have been devoted to the development of physical phantoms
  \citep{lin_validation_2001,campbell_flowbased_2005,perrin_validation_2005,fieremans_simulation_2008,tournier_resolving_2008}.
\cite{cote_tractometer_2013} conducted a thorough review of tractography methodologies using the
  so-called \emph{FiberCup} phantom \citep{poupon_new_2008,fillard_quantitative_2011}.
These phantoms are appropriate to evaluate the angular resolution in fiber crossings and accuracy of
  direction-independent scalar parameters in very simplistic geometries.
Since the complexity of whole-brain tractography is unaccountable with current materials and proposed
  methodologies to build physical phantoms, digital simulations are increasingly popular.
Early digital phantoms started with simulation of simple geometries as well
  \citep{basser_in_2000,goessl_fiber_2002,tournier_limitations_2002,leemans_mathematical_2005}
  to evaluate resolution of fiber crossings.
These tools generally implemented the multi-tensor model \citep{alexander_analysis_2001,tuch_high_2002}
  to simulate fiber crossing, fanning, kissing, etc.
\cite{close_software_2009} presented the \emph{Numerical Fibre Generator}, a software to simulate
  spherical shapes filled with digital fiber-tracts.
\cite{caruyer_Phantomas_2014} proposed \emph{Phantomas} to simulate any kind of analytic geometry
  inside a sphere.
\emph{Phantomas} models diffusion by a restricted and a hindered compartment, similar to
  \citep{assaf_composite_2005}.
\cite{wilkins_fiber_2014} proposed a whole-brain simulated phantom derived from voxel-wise orientation
  of fibers averaged from real \gls*{dmri} scans and the multi-tensor model with a compartment of
  isotropic diffusion.
Recently, \cite{neher_fiberfox_2014} proposed \emph{FiberFox}, a visualization software to develop
  complex geometries and their analytical description.
Once the geometries are obtained, the software generates the corresponding \gls*{dmri} signal with a
  methodology very close to that implemented in \emph{Phantomas}.

@@

\noindent\textbf{\textit{Data Generation\textcolon}\label{sec:data_generation}}
The methods to generate \emph{diffantoms} are rooted in the work of \cite{wilkins_fiber_2014}, and
  described in \autoref{fig:figure1}.
\emph{Diffantom} integrates two major improvements with respect to \citep{wilkins_fiber_2014}.
First, since we use a dataset from the \gls*{hcp} as input, data are corrected for the most relevant distortions.
\cite{wilkins_fiber_2014} explicitly state that their original data were not subjected to certain distortion
  corrections, and thus, generated data are affected correspondingly.
Second improvement is a more advanced signal model to generate the phantom using
  \emph{Phantomas} \citep{caruyer_Phantomas_2014}.

The simulation process begins with generating a microstructural model from real data (\autoref{fig:figure1}).
On one hand, the software requires up to five volume fractions $\{T_{1\,\cdots\,5}\}$ corresponding to the free-diffusion
  compartments that will be simulated.
These isotropic fraction maps use the \emph{5TT format} established with the latest version 3.0 of
  \emph{MRTrix} \citep{tournier_mrtrix_2012}, that describes the structure of the brain in the following
  order: \gls*{cgm}, \gls*{dgm}, \gls*{wm}, \gls*{csf}, and abnormal tissue.
Since we simulated a healthy subject, the last fraction map is empty and can be omitted.
On the other hand, the hindered-diffusion compartments are specified by up to three volume fractions $\{F_{1\,\cdots\,3}\}$
  of three single fiber populations per voxel along with their corresponding direction maps $\{V_{1\,\cdots\,3}\}$.

The process to obtain the microstructural model is described as follows:
1) The fiber orientation maps $\{V_{1\,\cdots\,3}\}$ and their corresponding fiber-fraction maps are
  obtained using the ball-and-stick model for multi-shell data of BEDPOSTX \citep{jbabdi_modelbased_2012}
  on the \gls*{dmri} data of a certain \gls*{hcp} subject.
2) We obtain a \gls*{fa} map after fitting a tensor model with \emph{MRTrix}.
3) The original fiber-fractions and the \gls*{fa} map are smoothed with a non-local means filter included
  in \emph{dipy} \citep{garyfallis_dipy_2011}.
4) By combining with \emph{MRTrix} the volume fraction maps computed with FSL FAST \citep{zhang_segmentation_2001} and
  FSL FIRST \citep{patenaude_bayesian_2011}, we obtain the macro-structural 5TT map of the subject.
5) The objects obtained in the previous steps are combined as described in the \nameref{sec:appendix} to generate the
  microstructural model, presented in \autoref{fig:figure1} box A.

Once a micro-structural model of the volume has been synthesized, a map of \glspl{fod} is computed using spherical
  convolution of the single fiber response and the fiber orientation maps $\{V_{1\,\cdots\,3}\}$, weighted by the
  corresponding fiber-fractions $\{F_{1\,\cdots\,3}\}$.
A close-up showing how the \glspl{fod} map looks is presented in \autoref{fig:figure1}.
The single fiber response is a Gaussian diffusion tensor with axial symmetry and eigenvalues $\lambda_1=$ 2.2\e{-3}
  and $\lambda_{2,3}=$ 0.2\e{-3} [mm$^2$s$^{-1}$].
The resulting \glspl{fod} map is then combined with the isotropic compartments corresponding to $\{T_{1\,\cdots\,5}\}$
  before generating the signal using \emph{Phantomas} \citep{caruyer_Phantomas_2014}.
By default, diffusion data are generated using a scheme of 100 directions distributed in one shell with uniform
  coverage \citep{caruyer_design_2013}.
Custom one- or multi-shell schemes can be generated supplying the tables of corresponding $b$-vectors and $b$-values.
Rician noise is also included in \emph{Phantomas}, and can be set by the user.
The default value for \gls*{snr} is preset to 90.0.
\Gls*{csf} was simulated with a unique compartment with isotropic diffusivity $D_{CSF}$ of 3.0\e{-3} [mm$^2$s$^{-1}$].
Conversely, \Gls*{wm} and \gls*{gm} included one isotropic compartment with $D_{WM} =$ 2.0\e{-4}, $D_{cGM} =$ 7.0\e{-4}
  and $D_{dGM} =$ 9.0\e{-4}, respectively [mm$^2$s$^{-1}$].
All these values for diffusivity (and the corresponding to the single-fiber response) can be modified by the user with
  custom settings.

@@

\noindent\textbf{\textit{Discussion\textcolon}}\label{sec:discussion} %
Whole-brain, realistic \gls*{dmri} phantoms are necessary in the developing field of structural
  connectomics.
The \emph{diffantom} is a derivative of \citep{wilkins_fiber_2014} in terms of methodology for
  simulation with two major improvements: the correctness of the \emph{minimally preprocessed} data
  \citep{glasser_minimal_2013} released within the \gls*{hcp}, and a more realistic diffusion
  model.
A possible competitor to \emph{diffantom} is the ground-truth data generated by the organizers of the
  Tractography Challenge held in the ISMRM 2015\footnote{\url{http://www.tractometer.org/ismrm_2015_challenge/}}.
Similarly to \emph{diffantom}, one \gls*{hcp} dataset is used as source of structural information.
However, in this case 25 fiber bundles were manually segmented to obtain a summary tractogram.
Then, making use of \emph{FiberFox}, the segmentation of each bundle is mapped to an analytical description
  which is fed into \emph{Phantomas}.
While this phantom is designed for the bundle-wise evaluation of tractography (with scores such as geometrical coverage,
  valid connections, invalid connections, missed connections, etc. \citep{cote_tractometer_2013}),
  \emph{diffantom} is intended for the connectome-wise evaluation of results, yielding tractography with
  a large number of bundles.
Therefore, \emph{diffantom} and \emph{FiberFox} are complementary as the hypotheses that can be investigated are different.
Moreover, \emph{diffantom} does not require costly manual segmentation of bundles, highly demanding in terms of physiology
  expertise and operation time.
This facilitates the use of \emph{diffantom} as a factory of whole-brain diffusion phantoms.
Lastly, since the gradient scheme can be set by the user, \emph{diffantom} can be seen as a mean to translate the so-called
  \emph{b-matrix} of the \gls*{hcp} to any target scheme.

@@

\section*{Data Sharing}
The first \emph{diffantom} is available under the \gls*{cc0} in {\color{red} (dryad?)}.
The associated software to ``\emph{diffantomize}'' real \gls*{dmri} data is available at \url{https://github.com/oesteban/diffantom}
  under an MIT license.
\emph{Phantomas} is available in \url{https://github.com/ecaruyer/Phantomas} under the revised-BSD license.

@@

\section*{Author Contributions}
All the authors contributed to this study.
OE designed the data generation procedure, implemented the processing pipelines and generated the example dataset.
EC implemented \emph{Phantomas} \citep{caruyer_Phantomas_2014}, helped integrate the project with the simulation routines.
OE, EC, AD thoroughly discussed and framed the aptness of the data in the community.
AD, MBC, MJLC, and AS interpreted the resulting datasets.
MBC, MJLC, and AS advised on all aspects of the study.

@@

\nolinenumbers
\bibliographystyle{frontiers/frontiersinSCNS_ENG_HUMS}
%\bibliographystyle{frontiersinHLTH&FPHY} % for Health and Physics articles
\bibliography{Remote}

@@

\glsresetall
\linenumbers
\section*{Appendix}\label{sec:appendix}
Let $\{T'_{1\,\cdots\,5}\}$ be the set of original fractions maps obtained with the combined use of FAST and FIRST, FA the
  \gls*{fa} map obtained from the original \gls*{dmri} data, and $\{V_{1\,\cdots\,3}, F'_{1\,\cdots\,3}\}$ the direction
  maps $V_i$ of restricted diffusion by fibers with their estimated volume fractions $F'_i$ calculated with BEDPOSTX.
The final $\{T_{1\,\cdots\,5}\}$ maps of isotropic fractions are computed as follows:

@@

\begin{figure}[h!]
\begin{center}
% \includegraphics[width=\linewidth]{figures/figure01A}
% \includegraphics[width=\linewidth]{figures/figure01B}
\includestandalone[width=\linewidth]{figure01}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:figure1} Figure \arabic{figure}. }%
{\textbf{Generation of \emph{diffantoms}:} First, a microstructural model is generated as described
  in the \nameref{sec:data_generation} subsection.
Please note the piece-wise linear function of the color scale to enable visibility of small volume fractions.
This microstructural model is fed into a simulation block that generates the final \gls*{dmri} dataset
  as described in the second block.
}
\end{figure}
